---
title: "p8105_hw6_ac4964"
author: "AnMei Chen"
date: "11/26/2021"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis" , 
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Load and clean the data for regression analysis

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = recode(babysex, "1" = "male", "2" = "female"),
    frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown"),
    malform = recode(malform, "0" = "absent", "1" = "present"),
    mrace = recode(mrace,"1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown")
  ) %>% 
  mutate(
    babysex = factor(babysex),
    frace = factor(frace),
    malform = factor(malform),
    mrace = factor(mrace)
    )

check_birthweight_na = sum(is.na(birthweight_df))
check_birthweight_na
```


Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. 

Since mother's age and weight, as well as the gestational age in weeks might affect baby's health, it is possible that these factors might influence baby's weight.In regression model 1, I will be analyzing the effects of these factors on birthweight.

```{r}
fit_1 = lm(bwt ~ momage + gaweeks + delwt, data = birthweight_df)
summary(fit_1)
summary(fit_1)$coef

fit_1 %>% 
  broom::tidy() %>% 
  select(term,estimate,p.value) %>% 
  knitr::kable(digits = 3)

birthweight_df %>% 
  modelr::add_residuals(fit_1) %>%
  modelr::add_predictions(fit_1) %>%  
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  geom_smooth(method = "lm")

```

Regression model using length at birth and gestational age as predictors (main effects only)

```{r}
birthweight_df %>% 
  ggplot(aes(x = blength, y = bwt)) +
  geom_point()

fit_2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
summary(fit_2)
summary(fit_2)$coef


fit_2 %>% 
  broom::tidy() %>% 
  select(term,estimate,p.value) %>% 
  knitr::kable(digits = 3)

birthweight_df = modelr::add_residuals(birthweight_df, fit_2)

birthweight_df %>% 
  modelr::add_residuals(fit_2) %>%
  modelr::add_predictions(fit_2) %>%  
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  geom_smooth(method = "lm")
```

Regression model using head circumference, length, sex, and all interactions (including the three-way interaction) between these.

```{r}

fit_3 = lm(bwt ~ bhead * blength + bhead * babysex + babysex *blength, data = birthweight_df) 
summary(fit_3)
summary(fit_3)$coef


fit_3 %>% 
  broom::tidy() %>% 
  select(term,estimate,p.value) %>% 
  knitr::kable(digits = 3)

birthweight_df %>% 
  modelr::add_residuals(fit_3) %>%
  modelr::add_predictions(fit_3) %>%  
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  geom_smooth(method = "lm")
```

Compare your model to two others in terms of the cross-validated prediction error.

```{r}
cv_df = crossv_mc(birthweight_df,100)

cv_df = 
  cv_df %>% 
  mutate(
    mod_1 = map(.x = train, ~lm(bwt ~ momage + gaweeks + delwt, data = .x)),
    mod_2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_3 = map(.x = train, ~lm(bwt ~ bhead * blength + bhead * babysex + babysex *blength, data = .x))
  ) %>% 
  mutate(
    rmse_1 = map2_dbl(.x = mod_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(.x = mod_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(.x = mod_3, .y = test, ~rmse(model = .x, data = .y))
  )

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```


## Problem 2

For this problem, we’ll use the 2017 Central Park weather data that we’ve seen elsewhere. The code chunk below (adapted from the course website) will download these data.
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words.
 
```{r}
weather_bootstrap_df =
  weather_df %>% 
  modelr::bootstrap(n = 5000)

weather_bootstrap_map_results =
  weather_bootstrap_df %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    r_squared_results = map(models, broom::glance),
    parameter_results = map(models, broom::tidy)
      ) 

log_parameter_results =
  weather_bootstrap_map_results %>% 
  select(parameter_results) %>% 
  unnest(parameter_results) %>%
  mutate(
    term = recode(term, `(Intercept)` = "intercept")
  ) %>% 
  select(term, estimate) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
    ) %>% 
  unnest(intercept,tmin) %>% 
  mutate(
    log_B0_B1 = log(intercept * tmin),
  ) 
  
log_parameter_dist =
  log_parameter_results %>% 
  ggplot(aes(x = log_B0_B1)) +
  geom_density()

r_squared_results =
  weather_bootstrap_map_results %>% 
  select(r_squared_results) %>% 
  unnest(r_squared_results) %>%   
  select(r.squared)

r_squared_dist =
  r_squared_results %>% 
  ggplot(aes(x = r.squared)) +
  geom_density()


```


Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂2
 and log(B0*B1)

```{r}

```

