---
title: "p8105_hw6_ac4964"
author: "AnMei Chen"
date: "11/26/2021"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis" , 
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Load and clean the data for regression analysis

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = recode(babysex, "1" = "male", "2" = "female"),
    frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown"),
    malform = recode(malform, "0" = "absent", "1" = "present"),
    mrace = recode(mrace,"1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown")
  ) %>% 
  mutate(
    babysex = factor(babysex),
    frace = factor(frace),
    malform = factor(malform),
    mrace = factor(mrace)
    )

check_birthweight_na = sum(is.na(birthweight_df))
check_birthweight_na
```


Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. 

```{r}
fit_1 = lm(bwt ~ momage + gaweeks + delwt, data = birthweight_df)
summary(fit_1)
summary(fit_1)$coef

fit_1 %>% 
  broom::tidy() %>% 
  select(term,estimate,p.value) %>% 
  knitr::kable(digits = 3)

birthweight_df %>% 
  modelr::add_residuals(fit_1) %>%
  modelr::add_predictions(fit_1) %>%  
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  geom_smooth(method = "lm")

```

Regression model using length at birth and gestational age as predictors (main effects only)

```{r}
birthweight_df %>% 
  ggplot(aes(x = blength, y = bwt)) +
  geom_point()

fit_2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
summary(fit_2)
summary(fit_2)$coef


fit_2 %>% 
  broom::tidy() %>% 
  select(term,estimate,p.value) %>% 
  knitr::kable(digits = 3)

birthweight_df = modelr::add_residuals(birthweight_df, fit_2)

birthweight_df %>% 
  modelr::add_residuals(fit_2) %>%
  modelr::add_predictions(fit_2) %>%  
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  geom_smooth(method = "lm")
```



```{r}

fit_3 = lm(bwt ~ bhead * blength + bhead * babysex + babysex *blength, data = birthweight_df) 
summary(fit_3)
summary(fit_3)$coef


fit_3 %>% 
  broom::tidy() %>% 
  select(term,estimate,p.value) %>% 
  knitr::kable(digits = 3)

birthweight_df %>% 
  modelr::add_residuals(fit_3) %>%
  modelr::add_predictions(fit_3) %>%  
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  geom_smooth(method = "lm")
```

Compare your model to two others in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

        

```{r}
cv_df = crossv_mc(birthweight_df,100)


cv_df = 
  cv_df %>% 
  mutate(
    mod_1 = map(.x = train, ~lm(bwt ~ momage + gaweeks + delwt, data = .x)),
    mod_2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_3 = map(.x = train, ~lm(bwt ~ bhead * blength + bhead * babysex + babysex *blength, data = .x))
  ) %>% 
  mutate(
    rmse_1 = map2_dbl(.x = mod_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(.x = mod_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(.x = mod_3, .y = test, ~rmse(model = .x, data = .y))
  )

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```


## Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}

```

